FLM for growth as function of SPEI

### 2021-01-27 analysis/paper/vital rate models.Rmd
added some EDA

```{r}
demog_post %>% ggplot(aes(x = surv)) + geom_bar() + facet_wrap(~habitat)
```
```{r}
demog_post %>% ggplot(aes(x = habitat, y = log_size)) + geom_boxplot()
```
```{r}
demog_post %>% ggplot(aes(x = flwr)) + geom_bar() + facet_wrap(~habitat)
```
# Speed up models with bam()

@@

```{r}
#mean survival
x <- demog_post$surv
sum(x, na.rm = TRUE) / length(x)
```

>>>>

```{r}
demog_post %>% ggplot(aes(x = surv)) + geom_bar() + facet_wrap(~habitat)
```

```{r}
demog_post %>% 
  group_by(habitat) %>% 
  summarize(surv = sum(surv, na.rm = TRUE) / n())
```

Survival nearly identical for 1 ha and CF.

```{r}
survival <-
  demog_post %>% 
  filter(habitat !="10-ha") %>% 
  group_by(year, habitat) %>% 
  summarize(surv = sum(surv, na.rm = TRUE)/n()) %>% 
  ggplot(aes(x = year, y = surv, color = habitat)) + geom_line()
survival / annotate_spei(spei)
```
Looks like survival went down year after 2003 drought and durring 2007 drought.

## Size / growth

```{r}
demog_post %>% ggplot(aes(x = habitat, y = log_size)) + geom_boxplot()
```

```{r}
size <- demog_post %>% 
  ggplot(aes(x = year, y = size, color = habitat)) +
  stat_summary(geom = "pointrange", fun.data = "mean_cl_boot") +
  stat_summary(geom = "line", fun = mean)

dates <- range(demog_post$year) %>% paste0(., "-01-01") %>% ymd()

spei <- ggplot(xa, aes(x = yearmonth, y = spei)) + 
  geom_line(aes(group = latlon)) +
  scale_x_yearmonth(limits = dates)
size/annotate_spei(spei)
```
Average plant size shrank in 2003 drought, but not 2007 drought

```{r}
demog_post %>% ggplot(aes(x = flwr)) + geom_bar() + facet_wrap(~habitat)
```
# Speed up models with bam()

@@
